---
title: "Bereavement Analysis"
format:
  html:
    embed-resources: true
editor: visual
author:
  - name: Jeremy Miles
    corresponding: true
  - name: Susanne Hempel
---

```{r}


library(dplyr)
library(glue)
library(knitr)
library(metafor)
library(quarto)
library(stringr)


load("kq.RData")
setwd(file_location)

```

```{r}
# Function exponentiates and coefficients for interpretation
GetExpCoefs <- function(fit) {
  cat("Estimate: ", round(exp(fit$b), 3), "\n")
  cat("Lower CI: ", round(exp(fit$ci.lb), 3), "\n")
  cat("Upper CI: ", round(exp(fit$ci.ub), 3), "\n")
  return(invisible(NULL))
}

cat("Check we have the right things.\n")
cat("Intervention: ", intervention, "\n")
table(d$KQ3)
table(d$KQ4)
table(d$intervention_type)

d <- d %>% 
  dplyr::mutate(
    ID = stringr::str_to_title(ID)
  ) %>%
  dplyr::arrange(ID) %>%
  dplyr::mutate(
    expected = ifelse(Expected.death == "Expected death", 1,
                      ifelse(Unexpected.death == "Unexpected death", 0, NA)),
    violent =  
      ifelse(Violent.death == "Violent death", 1,
             ifelse(Not.violent.death == "Not violent death", 0, NA)),
    adult = ifelse(age_subgroup_participants == "Adults", 1,
                   ifelse(age_subgroup_participants == "Pediatrics", 0, NA)),
    location_us = ifelse(location == "US", 1,
                         ifelse(location == "", NA, 0)),
    death_setting = ifelse(
      death_setting %in% c("Home", "Hospice", "Hospital"), death_setting, NA
    ),
    death_setting = 
      ifelse(death_setting == "Hospital", "At Hospital", death_setting),
    intervention_setting = 
      ifelse(
        setting %in% c(
          "Community", "Hospital", "Online", "Outpatient"
        ), setting, NA
      ),
    child_parent_spouse = 
      ifelse(
        Parent == "Parent" & Child == "" & Spouse == "", "Parent",
        ifelse(
          Parent == "" & Child == "Child" & Spouse == "", "Child", 
          ifelse(
            Parent == "" & Child == "" & Spouse == "Spouse", "Spouse", NA
          )
        )
      )
  )
```

```{r Calculate_Pooled_SD_Effect_Function}

CalculatePooledSDEffect <- function(
    model,
    data,
    var_prefix = NA
) {
  
  if (is.na(var_prefix)) {
    return("No var prefix provided.")
  }
  
  # extract standardized effect and CIs from model 
  std_effect <- coef(model)
  lower_ci <- model$ci.lb
  upper_ci <- model$ci.ub
  
  n1 <- sym(glue::glue("{var_prefix}_n_int_cont"))
  n2 <- glue::glue("{var_prefix}_n_ctrl_cont")
  sd1 <- sym(glue::glue("{var_prefix}_SD_ctrl_cont"))
  sd2 <- glue::glue("{var_prefix}_SD_int_cont")
  
  var <- glue::glue(var_prefix, "_measure_cont")
  
  d_pooled_sd <- data %>% 
    dplyr::mutate(
      pooled_var = 
        ((.data[[n1]] - 1) * .data[[sd1]]^2 + (.data[[n2]] - 1) * 
           .data[[sd2]]^2) /
        (.data[[n1]] + .data[[n2]] - 2)
    ) %>%
    # take the first 10 characters and convert to lower case of the scale
    dplyr::mutate(short_var = tolower(substr(!!rlang::sym(var), 1, 10))) %>%
    dplyr::group_by(
      short_var
    ) %>%
    dplyr::mutate(
      pooled_sd = sqrt(mean(pooled_var, na.rm = TRUE)
      ),
      n_studies = dplyr::n(),
      std_effect_model = std_effect,
      estimate_in_sds = pooled_sd * std_effect
    ) %>%
    dplyr::select(
      !!rlang::sym(var), short_var, n_studies, 
      pooled_sd, std_effect_model,
      estimate_in_sds
    ) %>%
    dplyr::distinct() %>%
    dplyr::arrange(short_var)
  
  cat(glue::glue("<h1>Effects in Original Scale</h1>\n"))
  
  d_pooled_sd <- d_pooled_sd %>%
    dplyr::mutate(
      std_effect = std_effect,
      estimate_in_sds = pooled_sd * std_effect,
      lower_ci = pooled_sd * lower_ci,
      upper_ci = pooled_sd * upper_ci,
    )
  
  knitr::kable(d_pooled_sd, digits = 3) %>% print()
  
}
```

```{r Analysis_Function}

source("RunAnalysisFunction.R")

```

\## Incidence of grief disorder: Incidence - Continuous

```{r}

outcome_description <- "Grief Disorder"
outcome_measure <- "grief_symp_measure_cont"

d_grief_disorder_incidence <- 
  metafor::escalc(
    m1i = incidence_grief_mean_int_cont,
    sd1i = incidence_grief_SD_int_cont,
    n1i = incidence_grief_n_int_cont,
    m2i = incidence_grief_mean_ctrl_cont,
    sd2i = incidence_grief_SD_ctrl_cont,
    n2i = incidence_grief_n_ctrl_cont,
    append = TRUE,
    measure = "SMD",
    data = d)

d_grief_disorder_incidence$ni <- attr(d_grief_disorder_incidence$yi, which = 'ni')


RunAnalysis(
  current_data = d_grief_disorder_incidence, 
  outcome_description = "Grief Disorder",
  outcome_measure = "grief_symp_measure_cont",
  var_prefix = "incidence_grief"
)

rm(d_grief_disorder_incidence)

```

\## Incidence of grief disorder: Incidence: Categorical

```{r}

d_incidence_grief_cat <- 
  metafor::escalc(
    ai = incidence_grief_counts_int_categ,
    bi = incidence_grief_n_int_categ - incidence_grief_counts_int_categ,
    ci = incidence_grief_counts_ctrl_categ,
    di = incidence_grief_n_ctrl_categ - incidence_grief_counts_ctrl_categ,
    measure = "RR",
    add = TRUE,
    data = d
  )

d_incidence_grief_cat$ni <- attr(d_incidence_grief_cat$yi, which = 'ni')

d_incidence_grief_cat$yi <- ifelse(
  d_incidence_grief_cat$incidence_grief_value_categ == "Higher is better", 
  d_incidence_grief_cat$yi * -1,
  d_incidence_grief_cat$yi
)

RunAnalysis(
  d_incidence_grief_cat, 
  outcome_description = "Incidence of Grief Disorder: Categorical",
  outcome_measure = "incidence_grief_measure_categ",
  categorical = TRUE,
  var_prefix = "incidence_grief"
)

rm(d_incidence_grief_cat)
```

\## Severity of grief disorder: Severity: Continuous

```{r}

# This code generates figure 2 and is reproduced in the kq_all_command_file.R
d_severity_grief <- metafor::escalc(
  m1i = severity_grief_mean_int_cont,
  sd1i = severity_grief_SD_int_cont,
  n1i = severity_grief_n_int_cont,
  m2i = severity_grief_mean_ctrl_cont,
  sd2i = severity_grief_SD_ctrl_cont,
  n2i = severity_grief_n_ctrl_cont,
  append = TRUE,
  measure = "SMD",
  data = d
)

d_severity_grief$ni <- attr(d_severity_grief$yi, which = 'ni')

RunAnalysis(
  current_data = d_severity_grief, 
  outcome_description = "Severity of grief disorder",
  outcome_measure = "severity_grief_measure_cont",
  var_prefix = "severity_grief",
  categorical = FALSE
)

rm(d_severity_grief)
```

\## Severity of grief disorder: Severity: Categorical

No control

```{r}


d_severity_grief_cat <- 
  metafor::escalc(
    ai = severity_grief_counts_int_categ,
    bi = severity_grief_n_int_categ - severity_grief_counts_int_categ,
    ci = severity_grief_counts_ctrl_categ,
    di = severity_grief_n_ctrl_categ - severity_grief_counts_ctrl_categ,
    measure = "RR",
    add = TRUE,
    data = d
  )

d_severity_grief_cat$ni <- attr(d_severity_grief_cat$yi, which = 'ni')

d_severity_grief_cat$yi <- ifelse(
  d_severity_grief_cat$severity_grief_value_categ   == "Higher is better", 
  d_severity_grief_cat$yi * -1,
  d_severity_grief_cat$yi
)


RunAnalysis(
  current_data = d_severity_grief_cat, 
  outcome_description = "Severity of Grief Disorder",
  outcome_measure = "severity_grief_measure_categ",
  categorical = TRUE
)

rm(d_severity_grief_cat)
```

\## Grief symptoms: Symptoms

```{r}
d_grief_symp <- metafor::escalc(
  m1i = grief_symp_mean_int_cont,
  sd1i = grief_symp_SD_int_cont,
  n1i = grief_symp_n_int_cont,
  m2i = grief_symp_mean_ctrl_cont,
  sd2i = grief_symp_SD_ctrl_cont,
  n2i = grief_symp_n_ctrl_cont,
  append = TRUE,
  measure = "SMD",
  data = d
)

d_grief_symp$ni <- attr(d_grief_symp$yi, which = 'ni')

d_grief_symp$yi <- ifelse(
  d_grief_symp$grief_symp_value == "Higher is better", 
  d_grief_symp$yi * -1,
  d_grief_symp$yi
)

RunAnalysis(
  d_grief_symp, 
  outcome_description = "Grief Symptoms",
  outcome_measure = "grief_symp_measure_cont",
  var_prefix = "grief_symp"
)

rm(d_grief_symp)

```

\## Grief symptoms: Symptoms Categorical

```{r}

d_grief_symp_cat <-
  metafor::escalc(
    ai = grief_symp_counts_int_categ,
    bi = grief_symp_n_int_categ - grief_symp_counts_int_categ,
    ci = grief_symp_counts_ctrl_categ,
    di = grief_symp_n_ctrl_categ - grief_symp_counts_ctrl_categ,
    measure = "RR",
    add = TRUE,
    data = d
  )

d_grief_symp_cat$ni <- attr(d_grief_symp_cat$yi, which = 'ni')

d_grief_symp_cat$yi <- ifelse(
  d_grief_symp_cat$grief_symp_value_categ == "Higher is better", 
  d_grief_symp_cat$yi * -1,
  d_grief_symp_cat$yi
)


RunAnalysis(
  current_data = d_grief_symp_cat, 
  outcome_description = "Grief Symptoms: Categorical",
  outcome_measure = "grief_symp_measure_categ",
  var_prefix = "grief_symp",
  categorical = TRUE
)

rm(d_grief_symp_cat)
```

\## Quality of life: QoL Continuous

```{r}

d_qol <- metafor::escalc(
  m1i = qol_mean_int_cont,
  sd1i = qol_SD_int_cont,
  n1i = qol_n_int_cont,
  m2i = qol_mean_ctrl_cont,
  sd2i = qol_SD_ctrl_cont,
  n2i = qol_n_ctrl_cont,
  append = TRUE,
  measure = "SMD",
  data = d
)

d_qol$ni <- attr(d_qol$yi, which = 'ni')

RunAnalysis(
  current_data = d_qol, 
  outcome_description = "QoL Continuous",
  outcome_measure = "qol_measure_cont",
  var_prefix = "qol"
)

rm(d_qol)
```

\## Quality of life: QoL Categorical

```{r}
d_qol_cat <-
  metafor::escalc(
    ai = qol_counts_int_categ,
    bi = qol_n_int_categ - qol_counts_int_categ,
    ci = qol_counts_ctrl_categ,
    di = qol_n_ctrl_categ - qol_counts_ctrl_categ,
    measure = "RR",
    add = TRUE,
    data = d
  )

d_qol_cat$ni <- attr(d_qol_cat$yi, which = 'ni')

RunAnalysis(
  d_qol_cat, 
  outcome_description = "QoL Categorical",
  outcome_measure = "qol_measure_categ",
  categorical = TRUE
)

rm(d_qol_cat)
```

\## Loneliness: Loneliness: Continuous

```{r}

d_loneliness <- metafor::escalc(
  m1i = loneliness_mean_int_cont,
  sd1i = loneliness_SD_int_cont,
  n1i = loneliness_n_int_cont,
  m2i = loneliness_mean_ctrl_cont,
  sd2i = loneliness_SD_ctrl_cont,
  n2i = loneliness_n_ctrl_cont,
  append = TRUE,
  measure = "SMD",
  data = d
)


d_loneliness$ni <- attr(d_loneliness$yi, which = 'ni')

RunAnalysis(
  d_loneliness, 
  outcome_description = "Loneliness",
  outcome_measure = "loneliness_measure_cont",
  var_prefix = "loneliness"
)

rm(d_loneliness)

```

\## Loneliness: Loneliness Categorical

```{r}


d_loneliness_cat <-
  try({
    metafor::escalc(
      ai = loneliness_counts_int_categ,
      bi = loneliness_n_int_categ - loneliness_counts_int_categ,
      ci = loneliness_counts_ctrl_categ,
      di = loneliness_n_ctrl_categ - loneliness_counts_ctrl_categ,
      measure = "RR",
      add = TRUE,
      data = d
    )
  })

d_loneliness_cat$ni <- attr(d_loneliness_cat$yi, which = 'ni')

RunAnalysis(
  d_loneliness_cat, 
  outcome_description = "Loneliness Categorical",
  outcome_measure = "loneliness_measure_categ",
  categorical = TRUE
)

rm(d_loneliness_cat)


```

\## Suicide Continuous

```{r}
d_suicide <- metafor::escalc(
  m1i = suicide_mean_int_cont,
  sd1i = suicide_SD_int_cont,
  n1i = suicide_n_int_cont,
  m2i = suicide_mean_ctrl_cont,
  sd2i = suicide_SD_ctrl_cont,
  n2i = suicide_n_ctrl_cont,
  append = TRUE,
  measure = "SMD",
  data = d
)

d_suicide$ni <- attr(d_suicide$yi, which = 'ni')

RunAnalysis(
  current_data = d_suicide, 
  outcome_description = "Suicide Continuous",
  outcome_measure = "suicide_measure_cont",
  var_prefix = "suicide"
)

rm(d_suicide)

```

\## Suicide categorical

```{r}
d_suicide_cat <-
  metafor::escalc(
    ai = suicide_counts_int_categ,
    bi = suicide_n_int_categ - suicide_counts_int_categ,
    ci = suicide_counts_ctrl_categ,
    di = suicide_n_ctrl_categ - suicide_counts_ctrl_categ,
    measure = "RR",
    add = TRUE,
    data = d
  )

d_suicide_cat$ni <- attr(d_suicide_cat$yi, which = 'ni')


RunAnalysis(
  current_data = d_suicide_cat, 
  outcome_description = "Suicide Categorical",
  outcome_measure = "suicide_measure_categ",
  categorical = TRUE
)

rm(d_suicide_cat)
```

\## Adverse health behaviors - Continuous

```{r}
d_adverse_health <- metafor::escalc(
  m1i = adverse_health_mean_int_cont,
  sd1i = adverse_health_SD_int_cont,
  n1i = adverse_health_n_int_cont,
  m2i = adverse_health_mean_ctrl_cont,
  sd2i = adverse_health_SD_ctrl_cont,
  n2i = adverse_health_n_ctrl_cont,
  append = TRUE,
  measure = "SMD",
  data = d
)

d_adverse_health$ni <- attr(d_adverse_health$yi, which = 'ni')



RunAnalysis(
  d_adverse_health, 
  outcome_description = "Adverse Health Behaviors - Continuous",
  outcome_measure = "adverse_health_measure_cont",
  var_prefix = "adverse_health"
)

rm(d_adverse_health)


```

\## Adverse health behaviors - Categorical

```{r}

d_adverse_health_cat <-
  metafor::escalc(
    ai = adverse_health_counts_int_categ,
    bi = 
      adverse_health_n_int_categ - adverse_health_counts_int_categ,
    ci = adverse_health_counts_ctrl_categ,
    di = adverse_health_n_ctrl_categ - adverse_health_counts_ctrl_categ,
    measure = "RR",
    add = TRUE,
    data = d
  )

d_adverse_health_cat$ni <- attr(d_adverse_health_cat$yi, which = 'ni')


RunAnalysis(
  d_adverse_health_cat, 
  outcome_description = "Adverse Health Behaviors - Categorical",
  outcome_measure = "adverse_health_measure_categ",
  categorical = TRUE
)

rm(d_adverse_health_cat)
```

\## Depression Continuous

```{r}
d_depression_symp <- metafor::escalc(
  m1i = depression_symp_mean_int_cont,
  sd1i = depression_symp_SD_int_cont,
  n1i = depression_symp_n_int_cont,
  m2i = depression_symp_mean_ctrl_cont,
  sd2i = depression_symp_SD_ctrl_cont,
  n2i = depression_symp_n_ctrl_cont,
  append = TRUE,
  measure = "SMD",
  data = d
)

d_depression_symp$ni <- attr(d_depression_symp$yi, which = 'ni')


d_depression_symp$yi <- ifelse(
  d_depression_symp$depression_symp_value  == "Higher is better", 
  d_depression_symp$yi * -1,
  d_depression_symp$yi
)

RunAnalysis(
  current_data = d_depression_symp, 
  outcome_description = "Depression - Continuous",
  outcome_measure = "depression_symp_measure_cont",
  var_prefix = "depression_symp"
)

rm(d_depression_symp)
```

\## Depression Categorical

```{r}
d_depression_symp_cat <-
  metafor::escalc(
    ai = depression_symp_counts_int_categ,
    bi = depression_symp_n_int_categ - depression_symp_counts_int_categ,
    ci = depression_symp_counts_ctrl_categ,
    di = depression_symp_n_ctrl_categ - depression_symp_counts_ctrl_categ,
    measure = "RR",
    add = TRUE,
    data = d
  )

d_depression_symp_cat$ni <- attr(d_depression_symp_cat$yi, which = 'ni')

d_depression_symp_cat$yi <- ifelse(
  d_depression_symp_cat$depression_symp_value_categ  == "Higher is better", 
  d_depression_symp_cat$yi * -1,
  d_depression_symp_cat$yi
)

RunAnalysis(
  d_depression_symp_cat, 
  outcome_description = "Depression - Categorical",
  outcome_measure = "depression_symp_measure_categ",
  categorical = TRUE
)

rm(d_depression_symp_cat)
```

\## Substance use

No substance use?

\## Unintended consequences: AE

No unintended

\#

\## Substance use

No substance use?

\## Unintended consequences: AE

No unintended
